%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{#1 \vspace{-2pt}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://stefanlance.com/}{\Large Stefan Lance}} &  \href{mailto:stefanlance@gmail.com}{stefanlance@gmail.com}\\
  \href{http://stefanlance.com/}{http://www.stefanlance.com} & +1-917-902-0509 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Chicago}{Chicago, IL}
      {B.S. in Mathematics}{Sep. 2013 -- Mar. 2017}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Twitter}{San Francisco, CA}
      {Software Engineer}{Sep. 2017 -- Present}
      \resumeItemListStart
        \resumeItem{Making the core libraries that power Twitter's distributed infrastructure more efficient and resilient.}
      \resumeItemListEnd

    \resumeSubheading
      {UChicago Computer Science Instructional Laboratory}{Chicago, IL}
      {Tutor}{Feb. 2015 -- Mar. 2017}
      \resumeItemListStart
        \resumeItem{Explained functional and imperative programming techniques in C and Racket to undergraduate students in introductory computer science courses.}
        \resumeItem{Assisted students and visitors with lab equipment (Ubuntu and Mac computers; printers; and projectors).}
      \resumeItemListEnd

    \resumeSubheading
      {Twitter}{San Francisco, CA}
      {Software Engineer Intern}{Jun. 2016 -- Sep. 2016}
      \resumeItemListStart
        \resumeItem{Wrote open source code for Finagle, Twitter's asynchronous Remote Procedure Call system.}
        \resumeItem{Developed a client-side admission control system to detect when server clusters are overloaded and back off from sending requests, with the goal of making Twitter's services more resilient to traffic spikes.}
      \resumeItemListEnd

    \resumeSubheading
      {Google Summer of Code}{Chicago, IL}
      {Student Participant}{Jun. 2015 -- Sep. 2015}
      \resumeItemListStart
        \resumeItem{Wrote three major features for Bundler 2.0, a dependency manager for Ruby projects.}
        \resumeItem{Built a user friendly file-based command configuration system to replace frail command line configuration code.}
        \resumeItem{Increased encapsulation by changing the default system-wide dependency installation path to be local.}
        \resumeItem{Implemented a system-wide cache for said dependencies to eliminate redundant installations and increase performance.}
      \resumeItemListEnd

    \resumeSubheading
      {UChicago Masters Program in Computer Science}{Chicago, IL}
      {Web Intern}{Jun. 2014 -- Sep. 2015}
      \resumeItemListStart
        \resumeItem{Developed and launched a Rails application which collects and organizes advisors' project proposals, students' applications, and advisors' evaluations of students.}
        \resumeItem{Developed and launched another Rails application which lets students request and enroll in courses.}
        \resumeItem{Eliminated the need for the program staff to manually manage and collect applications, course requests, and schedules.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
%\section{Projects}
%  \resumeSubHeadingListStart
%    \resumeSubItem{QuantSoftware Toolkit}
%      {Open source python library for financial data analysis and machine learning for finance.}
%    \resumeSubItem{Github Visualization}
%      {Data Visualization of Git Log data using D3 to analyze project trends over time.}
%    \resumeSubItem{Recommendation System}
%      {Music and Movie recommender systems using collaborative filtering on public datasets.}
%    \resumeSubItem{Mac Setup}
%      {Book that gives step by step instructions on setting up developer environment on Mac OS.}
%  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
  \resumeSubHeadingListStart
    \resumeItem{
      \textbf{Programming Languages}{: Scala, Ruby, Python, C, C++, Javascript}
      \hfill
      \textbf{Other Languages}{: HTML, CSS, SQL, Bash}
    }
    \resumeItem{
      \textbf{Tools \& Technologies}{: Unix, Git, PostgreSQL, SQLite, Subversion}
      \hfill
      \textbf{Frameworks}{: Rails, Jekyll, jQuery}
    }
  \resumeSubHeadingListEnd


%-------------------------------------------

%--------OTHER ACTIVITIES------------
\section{Technical Activities}
  \resumeSubHeadingListStart
    \resumeItem{Prepared undergraduate and graduate students for software engineering interviews via group whiteboarding sessions at UChicago's Tech Interview Workshop from Sep. 2016 until Mar. 2017.}
    \resumeItem{Trained for and competed in the International Collegiate Programming Competition qualifying round at the University of Chicago with two teammates in the spring of 2015.}
    \resumeItem{Actively participated in hack@uchicago by helping students with coding projects at weekly ``hack nights'' from Sep. 2013 until Apr. 2015.}
    \resumeItem{Collaborated with software engineers on Project Euler problems at weekly meetups from Jun. 2012 until Sep. 2013.}
    \resumeItem{Solved 85 Project Euler problems since 2012.}
  \resumeSubHeadingListEnd

\end{document}

%-------------------------------------------